### 2024-05-10 README.Rmd
Where they never never never

![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub R package version](https://img.shields.io/github/r-package/v/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)

@@

```{r example}
library(traveltime)
library(terra)
library(sdmtools)

friction_surface <- get_friction_surface(
    surface = "motor2020",
    file_name = temptif(),
    extent = matrix(
      data = c("111", "0", "112", 1),
      nrow = 2,
      ncol = 2,
      dimnames = list(
        c("x", "y"),
        c("min", "max")
      )
    )
  )

@@

travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here,
  file_name = temptif()
)

>>>>

![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
[![Lifecycle:](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub Downloads (all assets, all releases)](https://img.shields.io/github/downloads/geryan/traveltime/total)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)

Implements methods from Weiss et al. 2018, 2020 to calculate travel time from
given locations over a friction surface.

Citations:
D. J. Weiss, A. Nelson, C. A. Vargas-Ruiz, K. Gligoric, S., Bavadekar, E.
Gabrilovich, A. Bertozzi-Villa, J. Rozier, H. S. Gibson, T., Shekel, C. Kamath,
A. Lieber, K. Schulman, Y. Shao, V. Qarkaxhija, A. K. Nandi, S. H. Keddie, S.
Rumisha, P. Amratia, R. Arambepola, E. G. Chestnutt, J. J. Millar, T. L. Symons,
E. Cameron, K. E. Battle, S. Bhatt, and P. W. Gething. Global maps of travel
time to healthcare facilities. (2020) Nature Medicine.
https://doi.org/10.1038/s41591-020-1059-1

D. J. Weiss, A. Nelson, H.S. Gibson, W. Temperley, S. Peedell, A. Lieber, M.
Hancher, E. Poyart, S. Belchior, N. Fullman, B. Mappin, U. Dalrymple, J. Rozier,
T.C.D. Lucas, R.E. Howes, L.S. Tusting, S.Y. Kang, E. Cameron, D. Bisanzio, K.E.
Battle, S. Bhatt, and P.W. Gething. A global map of travel time to cities to
assess inequalities in accessibility in 2015. (2018). Nature.
doi:10.1038/nature25181.

@@

```{r example}
library(traveltime)
library(terra)

friction_surface <- get_friction_surface(
    surface = "motor2020",
    extent = matrix(
      data = c("111", "0", "112", 1),
      nrow = 2,
      ncol = 2,
      dimnames = list(
        c("x", "y"),
        c("min", "max")
      )
    )
  )

@@

travel_time <- calculate_travel_time(
  friction_surface = friction_surface,
  points = from_here
)
